Decoding Mortality: Trends and Causes in Canada between 2001-2022

### 2024-03-16 outputs/paper/paper.qmd
Updated references

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Decoding Mortality: Trends and Causes in Canada between 2001-2022"
subtitle: "A Bayesian Statistical Analysis Unveiling the Predominance of Malignant Neoplasms and Heart Diseases"
author: 
  - Yuchao Niu
thanks: "Code and data are available at: https://github.com/MelanieNiu/Canadian-Mortality."
date: today
date-format: long
abstract: "The study of mortality offers key public health insights into the fundamental causes and trends of death. This research investigates Canada's mortality trends from 2001 to 2022, employing Bayesian Poisson and negative binomial regression models to analyze data from the Canadian Vital Statistics Death Database. It reveals that malignant neoplasms and heart diseases significantly elevate mortality rates, surpassing the effects of unintentional accidents by five times and three times, respectively. Such findings highlight the critical necessity for targeted public health initiatives focusing on the prevention, early detection, and treatment of these conditions."
format: pdf
number-sections: true
bibliography: references.bib
---
